### 2018-04-13 report/cvpr2018RebuttalKit/latex/egrebuttal.tex
add report package

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{\LaTeX\ Guidelines for Author Response}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section{Introduction}

After receiving paper reviews, authors may optionally submit a rebuttal to address the reviewers' comments, which will be limited to a {\bf one page} PDF file.  Please follow the steps and style guidelines outlined below for submitting your author response.

Note that the author rebuttal is optional and, following similar guidelines to previous CVPR conferences, it is meant to provide you with an opportunity to rebut factual errors or to supply additional information requested by the reviewers. It is NOT intended to add new contributions (theorems, algorithms, experiments) that were not included in the original submission and were not requested by the reviewers. You may optionally add a figure, graph or proof to your rebuttal to better illustrate your answer to the reviewers' comments.

The rebuttal must adhere to the same blind-submission as the original submission and must comply with this rebuttal-formatted template.

%-------------------------------------------------------------------------

\subsection{Response length}
Author responses must be no longer than 1 page in length including any references and figures.  Overlength responses will simply not be reviewed.  This includes responses where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.  Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.

%------------------------------------------------------------------------
\section{Formatting your Response}

{\bf Make sure to update the paper title and paper ID in the appropriate place in the tex file.}

All text must be in a two-column format. The total allowable width of the text
area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54 cm) high.
Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch
(0.8 cm) space between them. The top margin should begin
1.0 inch (2.54 cm) from the top edge of the page.  The bottom margin should be
1-1/8 inches (2.86 cm) from the bottom edge of the page for $8.5 \times
11$-inch paper; for A4 paper, approximately 1-5/8 inches (4.13 cm) from the
bottom edge of the page.

Please number all of your sections and any displayed equations.  It is important
for readers to be able to refer to any particular equation.

Wherever Times is specified, Times Roman may also be used.  Main text should be
in 10-point Times, single-spaced. Section headings should be in 10 or 12 point
Times.  All paragraphs should be indented 1 pica (approx. 1/6 inch or 0.422
cm).  Figure and table captions should be 9-point Roman type as in
Figure~\ref{fig:onecol}.

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times, single-spaced,
at the end of your response. When referenced in the text, enclose the citation
number in square brackets, for example~\cite{Authors14}.  Where appropriate,
include the name(s) of editors of referenced books.

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{1.8in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you wish to make is resolvable in a printed copy of the response.  Resize fonts in figures to match the font in the body text, and choose line widths which render effectively in print.  Many readers (and reviewers), even of an electronic copy, will choose to print your response in order to read it.  You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the  figure width as a multiple of the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2018-04-13 report/proposal/proposal.tex
submit report

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{----} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Chinese Character Style Transfer with conditional GAN}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section{Introduction}

We propose a model which transforms a character from a typeface $A$ to another typeface $B$ given a few character pairs written in $A$ and $B$ respecitvely. We uses conditional GAN (cGAN) \cite{Authors01} to generate stylized character image with unaltered text meaning.

%-------------------------------------------------------------------------

\subsection{Motivation}
Unlike typefaces for English characters, it takes tremondous effort to design new Chinese typefaces. This is due to the simple fact that there are more than 4,000 commonly used Chinese characters \cite{Authors02} that have to be designed. Using this model, only a few reference style characters have to be designed manually. The model can generate the rest with consistent style.

%------------------------------------------------------------------------
\section{Related Work}

Some of the previous methods use backpropagation on an initial random noise image \cite{Authors03} or train a feedforward network \cite{Authors04} to transfer low-level texture style from a reference image to another. There are also exceptional result on articist or photorealistic image generation and translation using GANs and its derivatives \cite{Authors05}\cite{Authors06}.

%-------------------------------------------------------------------------
\section{Method}

\subsection{Formulation}
In this model, a generator $G$ and a discriminator $D$ will be trained. The given sample transform is $T:{A\to B}$ where $A$ and $B$ are small subset of the characters in two typefaces. $G$ will take $T$ and another character $C_A$ in typeface $A$ as input to generate an image $C_B$. $D$ then learns to discrimate between $C_B$ and other characters in typeface $B$ with $C_A$ as input.

Note that $C_A$ acts as the constraint vector in the cGAN such that the discriminator will be able to tell the difference between a transformed version of $C_A$ and a random character that has the appearance of typeface $B$. Without this constraint, \textit{model collapse} will happen as there are a lot of freedom in the Chinese character model.

\begin{figure}[t]
	\begin{center}
		\includegraphics[width=0.8\linewidth]{img.png}
	\end{center}
	\caption{Conditional GAN. Taken from \cite{Authors01} In our model, $C_A$ acts as the $y$ vector in the figure.}
	\label{fig:long}
	\label{fig:onecol}
\end{figure}

\subsection{Data}
There are abundant free Chinese fonts available online for download in .ttf format. The images of the characters can be extracted from the font file. A few of the typefaces will be reserved for testing and validation purposes. To make the generation more stable and the fact that we will generate $C_A$ automatically from character encodings, the typeface $A$ can be fixed. In this case, we consider using MingLiU, a common typeface that has clear strokes

{\small
\bibliographystyle{ieee}
\bibliography{bib}
}

\end{document}

### 2018-04-14 tff_reading_test.py
char img extraction

@@ -1,0 +1,24 @@
+import sys
+import os
+
+from PIL import Image, ImageFont, ImageDraw
+from matplotlib.pyplot import imshow
+
+image = Image.new("RGB", (128, 128), color=(1,1,1))
+draw = ImageDraw.Draw(image)
+
+path = "data/train/SentyTEA.ttf"
+
+font = ImageFont.truetype(path, 64)
+draw.text((0, 0), "的", font=font)
+
+font = ImageFont.truetype(path, 64)
+draw.text((64, 0), "而", font=font)
+
+font = ImageFont.truetype(path, 64)
+draw.text((0, 64), "繁", font=font)
+
+font = ImageFont.truetype(path, 64)
+draw.text((64, 64), "龍", font=font)
+
+image.show()

### 2018-05-01 font_loader.py
version 1

@@ -1,0 +1,79 @@
+import torch
+import torchvision
+from torch.utils.data import Dataset, DataLoader
+import numpy as np
+
+import os
+import random
+from font_reader import FontReader
+import collections
+
+def PILGrayToTensor(PILImage):
+    """
+    Defining this myself since torch.transform is weak
+    """
+    npArray = np.array(PILImage).astype('float32') / 255.0
+    return npArray[None, :, :]
+
+"""
+Load pairs of font for pytorch
+"""
+class FontDataset(Dataset):
+
+    def __init__(self, font_root, char_list, std_font_path, font_size, image_size):
+        self.font_root = font_root
+        self.font_reader_list = [FontReader(os.path.join(font_root, name), font_size, image_size)
+                                 for name in os.listdir(font_root)]
+
+        self.std_reader = FontReader(std_font_path, font_size, image_size)
+
+        # Remove characters that don't exist in one of the fonts
+        # Using hash to approximate
+        for reader in self.font_reader_list + [self.std_reader]:
+            # Get a hash value that appears more than a certain threshold -- let's say 3
+            recur_hash = 0
+            hash_dict = collections.defaultdict(int)
+            for char in char_list:
+                img = reader.get_image(char)
+                hash_val = hash(img.tobytes())
+                hash_dict[hash_val] += 1
+                if (hash_dict[hash_val] >= 3):
+                    recur_hash = hash_val
+                    break
+            # Remove all characters with such hash value
+            if (recur_hash != 0):
+                char_list = [x for x in char_list if hash(reader.get_image(x).tobytes()) != recur_hash]
+            print('Remaining characters: %d' % (len(char_list)))
+
+        self.char_list = char_list
+
+    def __len__(self):
+        return len(self.font_reader_list) * len(self.char_list)
+
+    def __getitem__(self, idx):
+        char_length = len(self.char_list)
+
+        char_idx = idx %  char_length
+        font_idx = idx // char_length
+
+        ref_char = random.choice(self.char_list)
+        tar_char = self.char_list[char_idx]
+
+        # Generate reference transform
+        transA = self.std_reader.get_image(ref_char)
+        transB = self.font_reader_list[font_idx].get_image(ref_char)
+
+        # Generate content reference
+        conRef = self.std_reader.get_image(tar_char)
+        # Generate ground truth
+        genGT = self.font_reader_list[font_idx].get_image(tar_char)
+
[…]

### 2018-05-01 font_reader.py

@@ -1,0 +1,38 @@
+from PIL import Image, ImageFont, ImageDraw
+import numpy as np
+
+from fontTools.ttLib import TTFont
+from fontTools.unicode import Unicode
+
+from itertools import chain
+
+class FontReader:
+
+    def __init__(self, font_path, font_size, image_size):
+        self.font = ImageFont.truetype(font_path, font_size*2)
+        self.font_size = font_size
+        self.image_size = image_size
+
+    def get_image(self, character):
+        """
+        Returns PIL image
+        """
+        # First draw once to find the center of mass
+        cg_image = Image.new("L", (self.image_size*4, self.image_size*4), color=(0))
+        cg_draw = ImageDraw.Draw(cg_image)
+        cg_draw.text((0, 0), character, (255), font=self.font)
+
+        try:
+            np_image = np.array(cg_image)
+            non_empty_col = np.nonzero(np_image.any(axis=0))[0]
+            non_empty_row = np.nonzero(np_image.any(axis=1))[0]
+            start_x = non_empty_col[0] - 1
+            last_x = non_empty_col[-1] + 1
+            start_y = non_empty_row[0] - 1 
+            last_y = non_empty_row[-1] + 1
+        except IndexError:
+            return Image.new("L", (self.image_size, self.image_size), color=(0))
+
+        cropped = cg_image.crop((start_x, start_y, last_x, last_y))
+
+        return cropped.resize((self.image_size, self.image_size))

### 2018-05-01 net.py

@@ -1,0 +1,331 @@
+import torch
+
+from torch.autograd import Variable
+import torch.nn as nn
+import torch.nn.functional as F
+import torch.optim as optim
+
+import time
+import os
+from visualdl import LogWriter
+import numpy as np
+
+import utils
+
+class Generator(nn.Module):
+    def __init__(self):
+        """
+        3 inputs - Transform: TA->TB and Reference content C
+        """
+        super(Generator, self).__init__()
+
+        self.convSet1 = nn.Sequential(
+            nn.Conv2d(3, 16, 3, padding=1),
+            nn.BatchNorm2d(16),
+            nn.ReLU(),
+            nn.Conv2d(16, 16, 3, padding=1),
+            nn.BatchNorm2d(16),
+            nn.ReLU()
+        )
+        self.pool1 = nn.MaxPool2d(2, 2, return_indices=True)
+
+        self.convSet2 = nn.Sequential(
+            nn.Conv2d(16, 32, 3, padding=1),
+            nn.BatchNorm2d(32),
+            nn.ReLU(),
+            nn.Conv2d(32, 32, 3, padding=1),
+            nn.BatchNorm2d(32),
+            nn.ReLU()
+        )
+        self.pool2 = nn.MaxPool2d(2, 2, return_indices=True)
+
+        self.convSet3 = nn.Sequential(
+            nn.Conv2d(32, 32, 3, padding=1),
+            nn.BatchNorm2d(32),
+            nn.ReLU()
+        )
+
+        self.unpool1 = nn.MaxUnpool2d(2, 2)
+        #With skip connection
+        self.deconvSet1 = nn.Sequential(
+            nn.Conv2d(32+32, 64, 3, padding=1),
+            nn.BatchNorm2d(64),
+            nn.ReLU(),
+            nn.Conv2d(64, 16, 3, padding=1),
+            nn.BatchNorm2d(16),
+            nn.ReLU()
+        )
+
+        self.unpool2 = nn.MaxUnpool2d(2, 2)
+        #With skip connection
+        self.deconvSet2 = nn.Sequential(
+            nn.Conv2d(16+1, 64, 3, padding=1),
+            nn.BatchNorm2d(64),
+            nn.ReLU(),
+            nn.Conv2d(64, 1, 3, padding=1),
+            nn.Sigmoid()
+        )
+
+    def forward(self, transformA, transformB, contentRef):
[…]

### 2018-05-01 test_batch_read.py

@@ -1,0 +1,35 @@
+from font_reader import FontReader
+from PIL import Image, ImageFont, ImageDraw
+import time
+
+batch_size = 100
+col_size = 10
+
+img_size = 48
+
+std_reader = FontReader('data/standard/mingliu.TTF', img_size-12, img_size)
+sty_reader = FontReader('data/train/NotoSansCJKtc-Light.otf', img_size-12, img_size)
+
+std_batch = Image.new("L", (img_size*batch_size//col_size, img_size*col_size), color=(0))
+sty_batch = Image.new("L", (img_size*batch_size//col_size, img_size*col_size), color=(0))
+
+with open('character_set/character_set_1798', 'r') as char_set:
+    char_batch = char_set.readlines()
+    char_batch = [x.strip() for x in char_batch] 
+
+    start = time.time()
+    for i in range(batch_size):
+        c = char_batch[i]
+        idx = i // col_size
+        idy = i % col_size
+
+        std_img = std_reader.get_image(c)
+        std_batch.paste(std_img, (img_size*idx, img_size*idy))
+
+        sty_img = sty_reader.get_image(c)
+        sty_batch.paste(sty_img, (img_size*idx, img_size*idy))
+
+    print(time.time() - start)
+
+std_batch.show()
+sty_batch.show()

### 2018-05-01 test_exist.py

@@ -1,0 +1,14 @@
+from itertools import chain
+import sys
+
+from fontTools.ttLib import TTFont
+from fontTools.unicode import Unicode
+
+font = TTFont(sys.argv[1])
+
+for cmap in font['cmap'].tables:
+    if cmap.isUnicode():
+        if ord('的') in cmap.cmap:
+            print('Exist')
+    
+print('end')

### 2018-05-01 tff_reading_test.py

@@ -3,22 +3,20 @@ import os
 
 from PIL import Image, ImageFont, ImageDraw
 from matplotlib.pyplot import imshow
+import numpy as np
+from scipy.ndimage.measurements import center_of_mass
 
-image = Image.new("RGB", (128, 128), color=(1,1,1))
+image = Image.new("L", (80, 80), color=(1))
 draw = ImageDraw.Draw(image)
 
-path = "data/train/SentyTEA.ttf"
-
+path = "data/train/wt004.ttf"
+#path = "data/train/NotoSansCJKtc-Light.otf"
 font = ImageFont.truetype(path, 64)
-draw.text((0, 0), "的", font=font)
 
-font = ImageFont.truetype(path, 64)
-draw.text((64, 0), "而", font=font)
+#w, h = draw.textsize("的", font=font)
+#draw.text((40-w/2, 40-h/2), "的", font=font)
 
-font = ImageFont.truetype(path, 64)
-draw.text((0, 64), "繁", font=font)
-
-font = ImageFont.truetype(path, 64)
-draw.text((64, 64), "龍", font=font)
+draw.text((0, 10), "的", (255),font=font)
+print(center_of_mass(np.array(image)))
 
 image.show()

### 2018-05-01 train.py

@@ -1,0 +1,28 @@
+from net import Net
+from font_loader import FontDataset
+
+import torch
+import torchvision
+import torchvision.transforms as transforms
+
+font_root = './data/limited/'
+std_font = './data/standard/mingliu.TTF'
+font_size = 52
+image_size = 48
+
+char_list_path = './character_set/character_set_1798'
+
+# Load the set of common characters
+with open(char_list_path, 'r') as char_set:
+    char_list = char_set.readlines()
+    char_list = [x.strip() for x in char_list] 
+
+train_batch_size = 128
+
+# Create dataset and dataloader
+train_dataset = FontDataset(font_root, char_list, std_font, font_size, image_size)
+train_loader = torch.utils.data.DataLoader(train_dataset, batch_size=train_batch_size,
+                                          shuffle=True, num_workers=2)
+
+net = Net(train_loader, 500, 10, 'model/BBResize')
+net.train()

### 2018-05-01 utils.py

@@ -1,0 +1,75 @@
+import os, gzip, torch
+import torch.nn as nn
+import numpy as np
+import scipy.misc
+import imageio
+import matplotlib.pyplot as plt
+from torchvision import datasets, transforms
+
+def save_images(images, size, image_path):
+    return imsave(images, size, image_path)
+
+def imsave(images, size, path):
+    image = np.squeeze(merge(images, size))
+    return scipy.misc.imsave(path, image)
+
+def merge(images, size):
+    h, w = images.shape[1], images.shape[2]
+    if (images.shape[3] in (3,4)):
+        c = images.shape[3]
+        img = np.zeros((h * size[0], w * size[1], c))
+        for idx, image in enumerate(images):
+            i = idx % size[1]
+            j = idx // size[1]
+            img[j * h:j * h + h, i * w:i * w + w, :] = image
+        return img
+    elif images.shape[3]==1:
+        img = np.zeros((h * size[0], w * size[1]))
+        for idx, image in enumerate(images):
+            i = idx % size[1]
+            j = idx // size[1]
+            img[j * h:j * h + h, i * w:i * w + w] = image[:,:,0]
+        return img
+    else:
+        raise ValueError('in merge(images,size) images parameter ''must have dimensions: HxW or HxWx3 or HxWx4')
+
+def generate_animation(path, num):
+    images = []
+    for e in range(num):
+        img_name = path + '_epoch%03d' % (e+1) + '.png'
+        images.append(imageio.imread(img_name))
+    imageio.mimsave(path + '_generate_animation.gif', images, fps=5)
+
+def loss_plot(hist, path = 'Train_hist.png', model_name = ''):
+    x = range(len(hist['D_loss']))
+
+    y1 = hist['D_loss']
+    y2 = hist['G_loss']
+
+    plt.plot(x, y1, label='D_loss')
+    plt.plot(x, y2, label='G_loss')
+
+    plt.xlabel('Iter')
+    plt.ylabel('Loss')
+
+    plt.legend(loc=4)
+    plt.grid(True)
+    plt.tight_layout()
+
+    path = os.path.join(path, model_name + '_loss.png')
+
+    plt.savefig(path)
+
+    plt.close()
+
+def initialize_weights(net):
+    for m in net.modules():
+        if isinstance(m, nn.Conv2d):
+            m.weight.data.normal_(0, 0.02)
+            m.bias.data.zero_()
[…]

### 2018-05-01 font_loader.py
next: add multiple context

@@ -8,6 +8,9 @@ import random
 from font_reader import FontReader
 import collections
 
+def PILGrayArrayToTensor(PILImageList):
+    return np.concatenate([PILGrayToTensor(x) for x in PILImageList], axis=0)
+
 def PILGrayToTensor(PILImage):
     """
     Defining this myself since torch.transform is weak
@@ -20,12 +23,13 @@ Load pairs of font for pytorch
 """
 class FontDataset(Dataset):
 
-    def __init__(self, font_root, char_list, std_font_path, font_size, image_size):
+    def __init__(self, font_root, char_list, std_font_path, font_size, image_size, numTransform):
         self.font_root = font_root
         self.font_reader_list = [FontReader(os.path.join(font_root, name), font_size, image_size)
                                  for name in os.listdir(font_root)]
 
         self.std_reader = FontReader(std_font_path, font_size, image_size)
+        self.numTransform = numTransform
 
         # Remove characters that don't exist in one of the fonts
         # Using hash to approximate
@@ -56,20 +60,23 @@ class FontDataset(Dataset):
         char_idx = idx %  char_length
         font_idx = idx // char_length
 
-        ref_char = random.choice(self.char_list)
-        tar_char = self.char_list[char_idx]
+        transA = self.numTransform*[None]
+        transB = self.numTransform*[None]
+        for i in range(self.numTransform):
+            ref_char = random.choice(self.char_list)
+            tar_char = self.char_list[char_idx]
 
-        # Generate reference transform
-        transA = self.std_reader.get_image(ref_char)
-        transB = self.font_reader_list[font_idx].get_image(ref_char)
+            # Generate reference transform
+            transA[i] = (self.std_reader.get_image(ref_char))
+            transB[i] = (self.font_reader_list[font_idx].get_image(ref_char))
 
         # Generate content reference
         conRef = self.std_reader.get_image(tar_char)
         # Generate ground truth
         genGT = self.font_reader_list[font_idx].get_image(tar_char)
 
-        transA = PILGrayToTensor(transA)
-        transB = PILGrayToTensor(transB)
+        transA = PILGrayArrayToTensor(transA)
+        transB = PILGrayArrayToTensor(transB)
         conRef = PILGrayToTensor(conRef)
         genGT = PILGrayToTensor(genGT)
 

### 2018-05-01 net.py

@@ -13,76 +13,114 @@ import numpy as np
 import utils
 
 class Generator(nn.Module):
-    def __init__(self):
+    def __init__(self, numTransform):
         """
         3 inputs - Transform: TA->TB and Reference content C
         """
         super(Generator, self).__init__()
 
-        self.convSet1 = nn.Sequential(
-            nn.Conv2d(3, 16, 3, padding=1),
-            nn.BatchNorm2d(16),
+        self.numTransform = numTransform
+
+        self.styleExtractor = nn.Sequential(
+            nn.Conv2d(2, 32, 3, padding=1),
+            nn.BatchNorm2d(32),
             nn.ReLU(),
-            nn.Conv2d(16, 16, 3, padding=1),
-            nn.BatchNorm2d(16),
+            nn.Conv2d(32, 32, 3, padding=1),
+            nn.BatchNorm2d(32),
+            nn.ReLU(),
+            nn.MaxPool2d(2, 2),
+
+            nn.Conv2d(32, 32, 3, padding=1),
+            nn.BatchNorm2d(32),
+            nn.ReLU(),
+            nn.Conv2d(32, 32, 3, padding=1),
+            nn.BatchNorm2d(32),
+            nn.ReLU(),
+            nn.MaxPool2d(2, 2),
+
+            nn.Conv2d(32, 32, 3, padding=1),
+            nn.BatchNorm2d(32),
+            nn.ReLU(),
+            nn.Conv2d(32, 1, 3, padding=1),
+        )
+
+        self.convSet1 = nn.Sequential(
+            nn.Conv2d(1, 32, 3, padding=1),
+            nn.BatchNorm2d(32),
+            nn.ReLU(),
+            nn.Conv2d(32, 32, 3, padding=1),
+            nn.BatchNorm2d(32),
             nn.ReLU()
         )
-        self.pool1 = nn.MaxPool2d(2, 2, return_indices=True)
+        self.pool1 = nn.MaxPool2d(2, 2)
 
         self.convSet2 = nn.Sequential(
-            nn.Conv2d(16, 32, 3, padding=1),
-            nn.BatchNorm2d(32),
-            nn.ReLU(),
-            nn.Conv2d(32, 32, 3, padding=1),
-            nn.BatchNorm2d(32),
-            nn.ReLU()
-        )
-        self.pool2 = nn.MaxPool2d(2, 2, return_indices=True)
-
[…]

### 2018-05-01 train.py

@@ -9,6 +9,7 @@ font_root = './data/limited/'
 std_font = './data/standard/mingliu.TTF'
 font_size = 52
 image_size = 48
+numTransform = 5
 
 char_list_path = './character_set/character_set_1798'
 
@@ -17,12 +18,12 @@ with open(char_list_path, 'r') as char_set:
     char_list = char_set.readlines()
     char_list = [x.strip() for x in char_list] 
 
-train_batch_size = 128
+train_batch_size = 64
 
 # Create dataset and dataloader
-train_dataset = FontDataset(font_root, char_list, std_font, font_size, image_size)
+train_dataset = FontDataset(font_root, char_list, std_font, font_size, image_size, numTransform)
 train_loader = torch.utils.data.DataLoader(train_dataset, batch_size=train_batch_size,
                                           shuffle=True, num_workers=2)
 
-net = Net(train_loader, 500, 10, 'model/BBResize')
+net = Net(train_loader, 500, 10, 'model/BBResize_S5T5_eN3', numTransform)
 net.train()

### 2018-05-01 font_loader.py
no trans A

@@ -23,17 +23,21 @@ Load pairs of font for pytorch
 """
 class FontDataset(Dataset):
 
-    def __init__(self, font_root, char_list, std_font_path, font_size, image_size, numTransform):
+    def __init__(self, font_root, char_list, std_root, font_size, image_size, numTransform, numRef):
         self.font_root = font_root
         self.font_reader_list = [FontReader(os.path.join(font_root, name), font_size, image_size)
                                  for name in os.listdir(font_root)]
 
-        self.std_reader = FontReader(std_font_path, font_size, image_size)
+        self.std_reader_list = [FontReader(os.path.join(std_root, name), font_size, image_size)
+                                 for name in os.listdir(std_root)]
+
         self.numTransform = numTransform
+
+        assert(len(self.std_reader_list) == numRef)
 
         # Remove characters that don't exist in one of the fonts
         # Using hash to approximate
-        for reader in self.font_reader_list + [self.std_reader]:
+        for reader in self.font_reader_list + self.std_reader_list:
             # Get a hash value that appears more than a certain threshold -- let's say 3
             recur_hash = 0
             hash_dict = collections.defaultdict(int)
@@ -60,27 +64,27 @@ class FontDataset(Dataset):
         char_idx = idx %  char_length
         font_idx = idx // char_length
 
-        transA = self.numTransform*[None]
+        #transA = self.numTransform*[None]
         transB = self.numTransform*[None]
         for i in range(self.numTransform):
             ref_char = random.choice(self.char_list)
             tar_char = self.char_list[char_idx]
 
             # Generate reference transform
-            transA[i] = (self.std_reader.get_image(ref_char))
+            #transA[i] = (self.std_reader_list[0].get_image(ref_char))
             transB[i] = (self.font_reader_list[font_idx].get_image(ref_char))
 
         # Generate content reference
-        conRef = self.std_reader.get_image(tar_char)
+        conRef = [x.get_image(tar_char) for x in self.std_reader_list]
         # Generate ground truth
         genGT = self.font_reader_list[font_idx].get_image(tar_char)
 
-        transA = PILGrayArrayToTensor(transA)
+        #transA = PILGrayArrayToTensor(transA)
         transB = PILGrayArrayToTensor(transB)
-        conRef = PILGrayToTensor(conRef)
+        conRef = PILGrayArrayToTensor(conRef)
         genGT = PILGrayToTensor(genGT)
 
         # numpy image: H x W x C
[…]

### 2018-05-01 net.py

@@ -13,7 +13,7 @@ import numpy as np
 import utils
 
 class Generator(nn.Module):
-    def __init__(self, numTransform):
+    def __init__(self, numTransform, numRef):
         """
         3 inputs - Transform: TA->TB and Reference content C
         """
@@ -22,63 +22,72 @@ class Generator(nn.Module):
         self.numTransform = numTransform
 
         self.styleExtractor = nn.Sequential(
-            nn.Conv2d(2, 32, 3, padding=1),
-            nn.BatchNorm2d(32),
-            nn.ReLU(),
-            nn.Conv2d(32, 32, 3, padding=1),
-            nn.BatchNorm2d(32),
-            nn.ReLU(),
-            nn.MaxPool2d(2, 2),
-
-            nn.Conv2d(32, 32, 3, padding=1),
-            nn.BatchNorm2d(32),
-            nn.ReLU(),
-            nn.Conv2d(32, 32, 3, padding=1),
-            nn.BatchNorm2d(32),
-            nn.ReLU(),
-            nn.MaxPool2d(2, 2),
-
-            nn.Conv2d(32, 32, 3, padding=1),
-            nn.BatchNorm2d(32),
-            nn.ReLU(),
-            nn.Conv2d(32, 1, 3, padding=1),
-        )
-
-        self.convSet1 = nn.Sequential(
             nn.Conv2d(1, 32, 3, padding=1),
             nn.BatchNorm2d(32),
             nn.ReLU(),
             nn.Conv2d(32, 32, 3, padding=1),
             nn.BatchNorm2d(32),
-            nn.ReLU()
-        )
-        self.pool1 = nn.MaxPool2d(2, 2)
+            nn.ReLU(),
+            nn.MaxPool2d(2, 2),
 
-        self.convSet2 = nn.Sequential(
-            nn.Conv2d(32, 64, 3, padding=1),
+            nn.Conv2d(32, 32, 3, padding=1),
+            nn.BatchNorm2d(32),
+            nn.ReLU(),
+            nn.Conv2d(32, 32, 3, padding=1),
+            nn.BatchNorm2d(32),
+            nn.ReLU(),
+            nn.MaxPool2d(2, 2),
+
+            nn.Conv2d(32, 32, 3, padding=1),
+            nn.BatchNorm2d(32),
+            nn.ReLU(),
+            nn.Conv2d(32, 32, 3, padding=1),
+            nn.BatchNorm2d(32),
[…]

### 2018-05-01 train.py

@@ -5,11 +5,13 @@ import torch
 import torchvision
 import torchvision.transforms as transforms
 
-font_root = './data/limited/'
-std_font = './data/standard/mingliu.TTF'
+font_root = './data/train/'
+std_font = './data/standard/'
 font_size = 52
 image_size = 48
-numTransform = 5
+
+numTransform = 10
+numRef = 5
 
 char_list_path = './character_set/character_set_1798'
 
@@ -21,9 +23,9 @@ with open(char_list_path, 'r') as char_set:
 train_batch_size = 64
 
 # Create dataset and dataloader
-train_dataset = FontDataset(font_root, char_list, std_font, font_size, image_size, numTransform)
+train_dataset = FontDataset(font_root, char_list, std_font, font_size, image_size, numTransform, numRef)
 train_loader = torch.utils.data.DataLoader(train_dataset, batch_size=train_batch_size,
                                           shuffle=True, num_workers=2)
 
-net = Net(train_loader, 500, 10, 'model/BBResize_S5T5_eN3', numTransform)
+net = Net(train_loader, 500, 10, 'model/BBResize_S5T5_eN3_NoRefA_train', numTransform, numRef)
 net.train()

### 2018-05-01 train.py
save

@@ -10,7 +10,7 @@ std_font = './data/standard/'
 font_size = 52
 image_size = 48
 
-numTransform = 10
+numTransform = 5
 numRef = 5
 
 char_list_path = './character_set/character_set_1798'
@@ -27,5 +27,5 @@ train_dataset = FontDataset(font_root, char_list, std_font, font_size, image_siz
 train_loader = torch.utils.data.DataLoader(train_dataset, batch_size=train_batch_size,
                                           shuffle=True, num_workers=2)
 
-net = Net(train_loader, 500, 10, 'model/BBResize_S5T5_eN3_NoRefA_train', numTransform, numRef)
+net = Net(train_loader, 500, 10, 'model/BBResize_S5T5_eN3_NoRefA_train_T5', numTransform, numRef)
 net.train()

### 2018-05-02 report/cvpr2018AuthorKit/latex/egpaper_final.tex
save1

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false,draft]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{----} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{1}
\begin{document}

%%%%%%%%% TITLE
\title{\LaTeX\ Chinese Character Style Transfer with conditional GAN}

\author{Ho Kei Cheng\\
Hong Kong University of Science and Technology\\
{\tt\small hkchengad@connect.ust.hk}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
	Image generation and style transfer have became a hot topic in research. 
	Generative Adversarial Networks (GANs) have been used to solve a lot of image generation
	problems. We here present an attempt at using GANs to perform style transfer by formulating
	it as an image generation problem on Chinese characters. Unlike most previous works, 
	our method does not focus on a singleton image transform. It learns how to transform an image
	to a unseen style by looking at font samples from the new style. Thus, no re-training is required
	to deal with novel fonts.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
The advancement of deep convolutional neural networks (DCNNs) has enabled computers
to better understand images at different abstraction levels. 
They are able to transfer the low level features like storkes and color
from an image to another, or even to generate images based on description.
Eariler studies on neural style transfer tries to minimize the difference 
between both the style and content of the source and target images using 
features from DCNN.

Recently, Generative Adversarial Networks (GANs) have also been used on
style transfer and image generation problems and have achieved success. GANs include both a generator and a discriminator. By imposing an additional discriminator as a guidance to the generator, GANs tend to generate more realistic images.

In this paper, we propose a style transfer GAN that can be used on multiple, unseen styles and content. The network is designed to extract content information and style information separately early on and combine them at a later stage.

We focus on style transfer for Chinese fonts. Traditionally it is difficult to design new Chinese fonts as there are more than 4,000 commonly used Chinese characters and all of them have to be designed manually. Our method aims to automatically generate the entire character set including thousands of characters given a few style references.

GANs include a generator 
and a discriminator having the objective function
\begin{align*}
\mathcal{L}_{GAN}(G, D)=&\mathbb{E}_{y}[\log(D(y))] +  \\&\mathbb{E}_{x,z}[\log(1-D(G(x,z))))]
\end{align*}
where the generator $G$ tries to minimize this objective while $D$ tries to maximize it.

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

\begin{figure*}
\begin{center}
\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
\end{center}
   \caption{Example of a short caption, which should be centered.}
\label{fig:short}
\end{figure*}

%------------------------------------------------------------------------
\section{Related Work}

\subsection{Image translation}
Image-to-image translation learns from paired images and attempts to establish the transformation from one image domain to another. It includes generating color images from grayscale images or converting day scene to night scene. Previous work like conditional GAN (cGAN), pix2pix and cycle-consistent adversarial network (CycleGAN) have shown appealing results in image translation. However, all of them are fixed to learn only one transformation at a time. To perform a new transform, the network must be retrained.

\subsection{Font Style Transfer}
A number of previous works have also studied the character style transfer process. "From A to Z" perform style transfer on English characters using variational autoencoder (VAE). A online project zi2zi borrows idea from pix2pix, using GAN with encoder-decoder and the U-net structure in the generator to perform font generation in a latent space created by some fixed font styles. Another work AEGN also uses GAN to generate calligraphy using a standard font directly. A more recent and aligned work is the EMD model, which separate the content and style representation using two distinct encoders.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
high.
Page numbers should be in footer with page numbers, centered and .75
inches from the bottom of the page and make it start at the correct page
number rather than the 4321 in the example.  To do this fine the line (around
line 23)
\begin{verbatim}
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\end{verbatim}
where the number 4321 is your assigned starting page.

Make sure the first page is numbered by commenting out the first page being
empty on line 46
\begin{verbatim}
%\thispagestyle{empty}
\end{verbatim}

%-------------------------------------------------------------------------
\subsection{Type-style and fonts}

Wherever Times is specified, Times Roman may also be used. If neither is
available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
the first page. The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
adverbs; do not capitalize articles, coordinate conjunctions, or
prepositions (unless the title begins with such a word). Leave two blank
lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type. This information is to
be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
inch or 0.422 cm). Make sure your text is fully justified---that is,
flush left and flush right. Please do not place any additional blank
lines between paragraphs.

Figure and table captions should be 9-point Roman type as in
Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-,
second-, and third-order headings.

FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
should be Times 12-point boldface, initially capitalized, flush left,
with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
should be Times 11-point boldface, initially capitalized, flush left,
with one blank line before, and one after. If you require a third-order
heading (we discourage it), use 10-point Times, boldface, initially
capitalized, flush left, preceded by one blank line, followed by a period
and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote {This is what a footnote looks like.  It
often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral
observations in
the text (within parentheses, if you prefer, as in this sentence).  If you
wish to use a footnote, place it at the bottom of the column on the page on
which it is referenced. Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times,
single-spaced, at the end of your paper. When referenced in the text,
enclose the citation number in square brackets, for
example~\cite{Authors14}.  Where appropriate, include the name(s) of
editors of referenced books.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Method & Frobnability \\
\hline\hline
Theirs & Frumpy \\
Yours & Frobbly \\
Ours & Makes one's heart Frob\\
\hline
\end{tabular}
\end{center}
\caption{Results.   Ours is better.}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you wish to
make is resolvable in a printed copy of the paper.  Resize fonts in figures
to match the font in the body text, and choose line widths which render
effectively in print.  Many readers (and reviewers), even of an electronic
copy, will choose to print your paper in order to read it.  You cannot
insist that they do otherwise, and therefore must not assume that they can
zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use
\verb+\includegraphics+, and to specify the  figure width as a multiple of
the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Please refer to the author guidelines on the CVPR 2018 web page for a discussion
of the use of color in your document.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit
your finished paper. We MUST have this form before your paper can be
published in the proceedings.

Please direct any questions to the production editor in charge of these
proceedings at the IEEE Computer Society Press: Phone (714) 821-8380, or
Fax (714) 761-1784.

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2018-05-02 font_loader.py

@@ -23,7 +23,7 @@ Load pairs of font for pytorch
 """
 class FontDataset(Dataset):
 
-    def __init__(self, font_root, char_list, std_root, font_size, image_size, numTransform, numRef):
+    def __init__(self, font_root, char_list, std_root, font_size, image_size, numTransform, numRef, forceChar=None):
         self.font_root = font_root
         self.font_reader_list = [FontReader(os.path.join(font_root, name), font_size, image_size)
                                  for name in os.listdir(font_root)]
@@ -32,6 +32,7 @@ class FontDataset(Dataset):
                                  for name in os.listdir(std_root)]
 
         self.numTransform = numTransform
+        self.forceChar = forceChar
 
         assert(len(self.std_reader_list) == numRef)
 
@@ -56,6 +57,8 @@ class FontDataset(Dataset):
         self.char_list = char_list
 
     def __len__(self):
+        if self.forceChar is not None:
+            return 1
         return len(self.font_reader_list) * len(self.char_list)
 
     def __getitem__(self, idx):
@@ -65,10 +68,13 @@ class FontDataset(Dataset):
         font_idx = idx // char_length
 
         #transA = self.numTransform*[None]
+        if self.forceChar is None:
+            tar_char = self.char_list[char_idx]
+        else:
+            tar_char = self.forceChar
         transB = self.numTransform*[None]
         for i in range(self.numTransform):
             ref_char = random.choice(self.char_list)
-            tar_char = self.char_list[char_idx]
 
             # Generate reference transform
             #transA[i] = (self.std_reader_list[0].get_image(ref_char))

### 2018-05-02 net.py

@@ -267,48 +267,31 @@ class Net(object):
                 D_real_loss = self.BCE_loss(D_real, D_real_vector)
 
                 # Generate fake data
-                # print('Stage 01')
                 G_out = self.G(transA, transB, reference)
-                # print('Stage 02')
                 D_fake = self.D(transA, transB, G_out, reference)
-                # print('Stage 03')
                 D_fake_loss = self.BCE_loss(D_fake, D_fake_vector)
-                # print('Stage 04')
 
                 D_loss = D_real_loss + D_fake_loss
-                # print('Stage 05')
                 
                 # Log result for D
                 # self.log_D_real_loss.add_record(running_idx, torch.sum(D_real_loss, 0))
-                # print('Stage 06')
                 # self.log_D_fake_loss.add_record(running_idx, torch.sum(D_fake_loss, 0))
-                # print('Stage 07')
                 # self.log_D_total_loss.add_record(running_idx, torch.sum(D_loss, 0))
-                # print('Stage 08')
 
                 # Update D's parameter
                 D_loss.backward()
-                # print('Stage 09')
                 self.D_optim.step()
-                # print('Stage 10')
 
                 # Train Generator
                 self.G_optim.zero_grad()
-                # print('Stage 11')
                 
                 # Compute Generator result
-                # print('Stage 0')
                 G_out = self.G(transA, transB, reference)
-                # print('Stage 1')
                 D_fake = self.D(transA, transB, G_out, reference)
-                # print('Stage 2')
 
                 G_D_loss = self.BCE_loss(D_fake, D_real_vector)
-                # print('Stage 3')
                 G_L1_loss = self.L1_Loss(G_out, groundTruth)
-                # print('Stage 4')
                 G_loss = G_D_loss + G_L1_loss
-                # print('Stage 5')
 
                 num_D_fake = D_fake_loss.mean()
                 num_D_real = D_real_loss.mean()
@@ -335,6 +318,28 @@ class Net(object):
             print('Epoch takes: %f' % (time.time() - epoch_start_time))
             if ((epoch+1) % self.save_epoch == 0):
                 self.save(epoch)
+
+    def generateOne(self):
+        for i, data in enumerate(self.data_loader, 0):
+            transA, transB, reference, groundTruth = data
+
+            if self.gpu_mode:
+                transB, reference, groundTruth = Variable(transB.cuda()), \
+                                                        Variable(reference.cuda()), \
+                                                        Variable(groundTruth.cuda())
+            else:
[…]

### 2018-05-02 test_single.py

@@ -1,0 +1,35 @@
+from net import Net
+from font_loader import FontDataset
+
+import torch
+import torchvision
+import torchvision.transforms as transforms
+
+font_root = './data/test1/'
+std_font = './data/standard/'
+font_size = 52
+image_size = 48
+
+numTransform = 5
+numRef = 5
+
+char_list_path = './character_set/character_set_1798'
+
+# Load the set of common characters
+with open(char_list_path, 'r') as char_set:
+    char_list = char_set.readlines()
+    char_list = [x.strip() for x in char_list] 
+
+# char_list = ['的']
+
+train_batch_size = 1
+
+# Create dataset and dataloader
+train_dataset = FontDataset(font_root, char_list, std_font, font_size, image_size, numTransform, numRef, '鬼')
+train_loader = torch.utils.data.DataLoader(train_dataset, batch_size=train_batch_size,
+                                          shuffle=True, num_workers=1)
+
+net = Net(train_loader, 500, 10, 'model/BBResize_S5T5_eN3_NoRefA_train_T5', numTransform, numRef)
+
+net.load(389)
+net.generateOne()

### 2018-05-02 report/cvpr2018AuthorKit/latex/egpaper_final.tex
almost there

@@
 %%%%%%%%% TITLE
-\title{\LaTeX\ Chinese Character Style Transfer with conditional GAN}
+\title{Chinese Character Style Transfer with conditional GAN}
 
@@
 between both the style and content of the source and target images using 
-features from DCNN.
+features from DCNN. \cite{DBLP:journals/corr/JohnsonAL16} \cite{Authors04} \cite{Authors03}
 
@@
 By imposing an additional discriminator as a guidance to the generator, GANs tend to generate more realistic images.
+GANs include a generator and a discriminator having the objective function
+\begin{align*}
+\mathcal{L}_{GAN}(G, D)=&\mathbb{E}_{y}[\log(D(y))] +  \\&\mathbb{E}_{x,z}[\log(1-D(G(x,z))))]
+\end{align*}
+where the generator $G$ tries to minimize this objective while $D$ tries to maximize it. \cite{DBLP:journals/corr/RadfordMC15}
 
@@
 We focus on style transfer for Chinese fonts.
-Traditionally it is difficult to design new Chinese fonts as there are more than 4,000 commonly used Chinese characters and all of them have to be designed manually.
+Traditionally it is difficult to design new Chinese fonts as there are more than 4,000 commonly used Chinese characters and all of them have to be designed manually \cite{Authors02}.
 Our method aims to automatically generate the entire character set including thousands of characters given a few style references.
-
-GANs include a generator 
-and a discriminator having the objective function
-\begin{align*}
-\mathcal{L}_{GAN}(G, D)=&\mathbb{E}_{y}[\log(D(y))] +  \\&\mathbb{E}_{x,z}[\log(1-D(G(x,z))))]
-\end{align*}
-where the generator $G$ tries to minimize this objective while $D$ tries to maximize it.
-
-\begin{figure}[t]
-\begin{center}
-\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-\end{center}
-   \caption{Example of caption.  It is set in Roman so that mathematics
-   (always set in Roman: $B \sin A = A \sin B$) may be included without an
-   ugly clash.}
-\label{fig:long}
-\label{fig:onecol}
-\end{figure}
-
-\begin{figure*}
-\begin{center}
-\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-\end{center}
-   \caption{Example of a short caption, which should be centered.}
-\label{fig:short}
-\end{figure*}
 
@@
 It includes generating color images from grayscale images or converting day scene to night scene.
-Previous work like conditional GAN (cGAN), pix2pix and cycle-consistent adversarial network (CycleGAN) have shown appealing results in image translation.
+Previous work like conditional GAN (cGAN) \cite{Authors01}, pix2pix\cite{DBLP:journals/corr/IsolaZZE16} and cycle-consistent adversarial network (CycleGAN)\cite{DBLP:journals/corr/ZhuPIE17} have shown appealing results in image translation.
 However, all of them are fixed to learn only one transformation at a time.
@@
 A number of previous works have also studied the character style transfer process.
-"From A to Z" perform style transfer on English characters using variational autoencoder (VAE).
+"From A to Z" perform style transfer on English characters using variational autoencoder (VAE) \cite{DBLP:journals/corr/UpchurchSB16}.
 A online project zi2zi borrows idea from pix2pix, using GAN with encoder-decoder and the U-net structure in the generator to perform font generation in a latent space created by some fixed font styles.
-Another work AEGN also uses GAN to generate calligraphy using a standard font directly.
-A more recent and aligned work is the EMD model, which separate the content and style representation using two distinct encoders.
-
-%-------------------------------------------------------------------------
-\subsection{Margins and page numbering}
-
-All printed material, including text, illustrations, and charts, must be kept
-within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
-high.
-Page numbers should be in footer with page numbers, centered and .75
-inches from the bottom of the page and make it start at the correct page
-number rather than the 4321 in the example.  To do this fine the line (around
-line 23)
-\begin{verbatim}
-%\ifcvprfinal\pagestyle{empty}\fi
-\setcounter{page}{4321}
-\end{verbatim}
-where the number 4321 is your assigned starting page.
-
-Make sure the first page is numbered by commenting out the first page being
-empty on line 46
-\begin{verbatim}
-%\thispagestyle{empty}
-\end{verbatim}
-
-%-------------------------------------------------------------------------
-\subsection{Type-style and fonts}
-
-Wherever Times is specified, Times Roman may also be used. If neither is
-available on your word processor, please use the font closest in
-appearance to Times to which you have access.
-
-MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
-the first page. The title should be in Times 14-point, boldface type.
-Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
-adverbs; do not capitalize articles, coordinate conjunctions, or
-prepositions (unless the title begins with such a word). Leave two blank
-lines after the title.
-
-AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
-and printed in Times 12-point, non-boldface type. This information is to
-be followed by two blank lines.
-
-The ABSTRACT and MAIN TEXT are to be in a two-column format.
-
-MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
-double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
-inch or 0.422 cm). Make sure your text is fully justified---that is,
-flush left and flush right. Please do not place any additional blank
-lines between paragraphs.
-
-Figure and table captions should be 9-point Roman type as in
-Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.
-
-\noindent Callouts should be 9-point Helvetica, non-boldface type.
-Initially capitalize only the first word of section titles and first-,
-second-, and third-order headings.
-
-FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
-should be Times 12-point boldface, initially capitalized, flush left,
-with one blank line before, and one blank line after.
-
-SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
-should be Times 11-point boldface, initially capitalized, flush left,
-with one blank line before, and one after. If you require a third-order
-heading (we discourage it), use 10-point Times, boldface, initially
-capitalized, flush left, preceded by one blank line, followed by a period
-and your text on the same line.
-
-%-------------------------------------------------------------------------
-\subsection{Footnotes}
-
-Please use footnotes\footnote {This is what a footnote looks like.  It
-often distracts the reader from the main flow of the argument.} sparingly.
-Indeed, try to avoid footnotes altogether and include necessary peripheral
-observations in
-the text (within parentheses, if you prefer, as in this sentence).  If you
-wish to use a footnote, place it at the bottom of the column on the page on
-which it is referenced. Use Times 8-point type, single-spaced.
-
-%-------------------------------------------------------------------------
-\subsection{References}
-
-List and number all bibliographical references in 9-point Times,
-single-spaced, at the end of your paper. When referenced in the text,
-enclose the citation number in square brackets, for
-example~\cite{Authors14}.  Where appropriate, include the name(s) of
-editors of referenced books.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{|l|c|}
-\hline
-Method & Frobnability \\
-\hline\hline
-Theirs & Frumpy \\
-Yours & Frobbly \\
-Ours & Makes one's heart Frob\\
-\hline
-\end{tabular}
-\end{center}
-\caption{Results.   Ours is better.}
-\end{table}
-
-%-------------------------------------------------------------------------
-\subsection{Illustrations, graphs, and photographs}
-
-All graphics should be centered.  Please ensure that any point you wish to
-make is resolvable in a printed copy of the paper.  Resize fonts in figures
-to match the font in the body text, and choose line widths which render
-effectively in print.  Many readers (and reviewers), even of an electronic
-copy, will choose to print your paper in order to read it.  You cannot
-insist that they do otherwise, and therefore must not assume that they can
-zoom in to see tiny details on a graphic.
-
-When placing figures in \LaTeX, it's almost always best to use
-\verb+\includegraphics+, and to specify the  figure width as a multiple of
-the line width as in the example below
-{\small\begin{verbatim}
-   \usepackage[dvips]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]
-                   {myfile.eps}
-\end{verbatim}
-}
-
-%-------------------------------------------------------------------------
-\subsection{Color}
-
-Please refer to the author guidelines on the CVPR 2018 web page for a discussion
-of the use of color in your document.
+Another work AEGN also uses GAN to generate calligraphy using a standard font directly \cite{DBLP:journals/corr/LyuBYZHL17}.
+A more recent and aligned work is the EMD model, which separate the content and style representation using two distinct encoders \cite{DBLP:journals/corr/abs-1711-06454}.
 
 %------------------------------------------------------------------------
-\section{Final copy}
+\section{Method}
+Our model consists of two parts: \textit{Generator} and \textit{Discriminator}.
+The generator will be feed with reference context and reference style, trying to generate the character in the said context with the given style.
+The disciminator then tries to distinguish generated characters with ground truths.
 
-You must include your signed IEEE copyright release form when you submit
-your finished paper. We MUST have this form before your paper can be
-published in the proceedings.
+\begin{figure*}
+	\begin{center}
+		\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
+	\end{center}
+	\caption{The network structure}
+	\label{fig:short}
+\end{figure*}
 
-Please direct any questions to the production editor in charge of these
-proceedings at the IEEE Computer Society Press: Phone (714) 821-8380, or
-Fax (714) 761-1784.
+\subsection{Generator}
+The generator consists of two encoders and a decoder.
+The two encoders are \textit{Style Encoder} and \textit{Context Encoder} respectively.
+All the reference context will be concatenated together and fed into the context encoder.
+The styles will be fed one by one into the style encoder.
+
+After all the contexts and styles have been encoded, they are concatenated together and passed to the decoder network. The output from the decoder network is the generated result.
+
+\subsubsection{Encoder}
+Both the \textit{Style Encoder} and \textit{Context Encoder} consist of layers of $3x3Convolution - BatchNorm - ReLU$.
+Max-poolings are used to reduce the dimension of the original $64*64$ input to $8*8$ encoded output.
+
+\subsubsection{Decoder}
+To enchance the quaility of generated images, transposed convolutions (also known as deconvolution) are used to upsample the encoded context and style reference, as suggested by DCGAN\cite{DBLP:journals/corr/RadfordMC15}.
+The decoder network is a transposed version of the encoder, except that transposed convolution with input padding of 2 and output padding of 1 has replaced max-poolings.
+
+There are U-Net\cite{DBLP:journals/corr/RonnebergerFB15} like structure which connect the encoder and decoder together with skip-connection to preverse some of the lost information in max-pooling.
+
+\subsection{Discriminator}
+There are two small networks in the discriminator.
+They are the  \textit{Context Discriminator} and \textit{Style Discriminator} respectively.
+The context discriminator takes the image-to-be tested with the context reference to determine its realness in terms of context.
+The style discriminator take the style reference instead, and compare realness in terms of style.
+Their results are averaged to obtain overall discriminator score.
+
+\subsection{Losses}
+We have used the binary cross entropy loss to update the discriminator, guiding it to output 1 for ground truth images and 0 for generated images.
+
+For the generator, both binary cross entropy loss and L1 loss is used as suggested by pix2pix.
+The binary cross entropy loss guides the generator to output images that the discriminator will give high score, i.e.
+to fool the discriminator.
+The L1 loss compare the generator's output and the ground truth image.
+
+\section{Result}
+The network can successfully generate readable characters that have similar low-level features as ground truths. However, there are a few issues:
+
+\begin{enumerate}
+	\item Thins stroke might be missing.
+	\item The generated image looks "dirty", i.e. has noises.
+	\item It failed to learn high level features like spacing between strokes.
+\end{enumerate}
+
+\begin{figure}[t]
+	\begin{center}
+		\includegraphics[width=0.8\linewidth]{385gen.png}
+		\includegraphics[width=0.8\linewidth]{385gt.png}
+		\includegraphics[width=0.8\linewidth]{385r1.png}
+	\end{center}
+	\caption{Generating different characters in different fonts in a single batch. Top to bottom: Generated characters, ground truth and one of the context reference}
+	\label{fig:long}
+	\label{fig:onecol}
+\end{figure}
+
+\begin{figure}[t]
+	\begin{center}
+		\includegraphics[width=0.8\linewidth]{380gen.png}
+		\includegraphics[width=0.8\linewidth]{380gt.png}
+		\includegraphics[width=0.8\linewidth]{380r1.png}
+	\end{center}
+	\caption{Another result. Top to bottom: Generated characters, ground truth and one of the context reference}
+	\label{fig:long}
+	\label{fig:onecol}
+\end{figure}
+
+\section{Implementation and data}
+The model is implementated with PyTorch. It is trained with SGD with learning rate $0.001$, momentum of $0.9$ and batch size $64$ for 400 epochs. The training took 15 hours on a GTX970.
+
+31 fonts are obtained onlined.
+23 of them are used in style reference training, 5 of them used as context reference and the rest act as test set.
+1702 commonly used Chinese characters are picked to be used in training.
+
+Note that different fonts can have significant difference in size and position even when the same font size and origin is used. Preprocessing is done so that the bounding box of each character aligns.
 

### 2018-05-02 report/final/egpaper_final.tex
clean up

--- 2018-05-02 report/cvpr2018AuthorKit/latex/egpaper_final.tex
@@
 "From A to Z" perform style transfer on English characters using variational autoencoder (VAE) \cite{DBLP:journals/corr/UpchurchSB16}.
-A online project zi2zi borrows idea from pix2pix, using GAN with encoder-decoder and the U-net structure in the generator to perform font generation in a latent space created by some fixed font styles.
+A online project zi2zi\cite{zi2zi} borrows idea from pix2pix, using GAN with encoder-decoder and the U-net structure in the generator to perform font generation in a latent space created by some fixed font styles.
 Another work AEGN also uses GAN to generate calligraphy using a standard font directly \cite{DBLP:journals/corr/LyuBYZHL17}.
@@
 	\begin{center}
-		\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
+		\includegraphics[width=0.8\linewidth]{gen.png}
 	\end{center}
-	\caption{The network structure}
+	\caption{The Generator structure}
+	\label{fig:short}
+\end{figure*}
+
+\begin{figure*}
+	\begin{center}
+		\includegraphics[width=0.8\linewidth]{dis.png}
+	\end{center}
+	\caption{The Discriminator structure}
 	\label{fig:short}

### 2018-05-03 report/final/egpaper_final.tex
fix typo

@@
 Another work AEGN also uses GAN to generate calligraphy using a standard font directly \cite{DBLP:journals/corr/LyuBYZHL17}.
-A more recent and aligned work is the EMD model, which separate the content and style representation using two distinct encoders \cite{DBLP:journals/corr/abs-1711-06454}.
+A more recent and aligned work is the EMD model, which separates the content and style representation using two distinct encoders \cite{DBLP:journals/corr/abs-1711-06454}.
 
@@
 
-There are U-Net\cite{DBLP:journals/corr/RonnebergerFB15} like structure which connect the encoder and decoder together with skip-connection to preverse some of the lost information in max-pooling.
+There is U-Net\cite{DBLP:journals/corr/RonnebergerFB15} like structure which connects the encoder and decoder together with skip-connection to preverse some of the lost information in max-pooling.
 
@@
 
-For the generator, both binary cross entropy loss and L1 loss is used as suggested by pix2pix.
+For the generator, both binary cross entropy loss and L1 loss are used as suggested by pix2pix.
 The binary cross entropy loss guides the generator to output images that the discriminator will give high score, i.e.
 to fool the discriminator.
-The L1 loss compare the generator's output and the ground truth image.
+The L1 loss compares the generator's output with the ground truth image.
 
@@
 \begin{enumerate}
-	\item Thins stroke might be missing.
+	\item Thin strokes might be missing.
 	\item The generated image looks "dirty", i.e. has noises.
@@
 
-31 fonts are obtained onlined.
+31 fonts are obtained online.
 23 of them are used in style reference training, 5 of them used as context reference and the rest act as test set.
